
\centerline{\Large\bf Jefferson Lab Hall A Collaboration}
\vskip 0.3in

\begin{center}
%
\vskip 0.15in
K.~Aniol \\
{\it Cal State University, Los Angeles, California}
\vskip 0.15in
G.B.~Franklin, B.~Quinn \\
 {\it Carnegie Mellon University, Pittsburgh, Pennsylvania} 
%
\vskip 0.15in
C.~Chen, Nuruzzaman, L.~Tang \\
{\it Hampton University, Hampton, Virginia}
%
\vskip 0.15in
A.~J.~R. ~Puckett~(Co-Spokesperson) \\
{\it University of Connecticut,  Storrs, Connecticut.}
%
\vskip 0.15in
X.~Jiang~(Co-Spokesperson)\footnote{Contact person. Email: jiang@jlab.org}  \\
 {\it  Los Alamos National Laboratory, Los Alamos, New Mexico.}
%
\vskip 0.15in
A.~Ahmidouch, S.~Danagoulian \\
{\it North Carolina A\&T State University, Greensboro, North Carolina}
%
\vskip 0.15in
W.~Korsch \\
{\it University of Kentucky, Lexington, Kentucky.}
%
\vskip 0.15in
T.~Holmstrom \\
{\it Longwood University, Farmville, Virginia}
%
\vskip 0.15in
L.~El~Fassi,  C.~E. Hyde \\
{\it Old Dominion University, Norfolk, Virginia}
\vskip 0.15in
R.~Gilman,  K.~M.~Mesick,  R.~Ransome \\
{\it Rutgers University, Piscataway, New Jersey.}
%
\vskip 0.15in
D.~Higinbotham, M.~Jones, C.~Keppel,  B.~Wojtsekhowski  \\
{\it  Thomas Jefferson National Accelerator Facility, Newport News, Virginia.}
%
\vskip 0.15in
X.~Bai,  G.~Cates, D.~Day, D.~Di, K~.Gnanvo,  C.~Gu, N.~Liyanage ~(Co-Spokesperson), V.~Nelyubin, H.~Nguyen, O.~Rondon  \\ 
%  
{\it University of Virginia, Charlottesville, Virginia.}
%
\vskip 0.15in
T.~Averett \\
{\it  College of William and Mary, Williamsburg, Virginia.}
%
\vskip 0.15in
V. ~Bellini \\
{\it University and INFN Ð Catania, Italy.}
\vskip 0.15in
E.~Cisbani \\ 
{\it INFN Roma--I, Italy.}  
%
\vskip 0.15in
J.~Beri\v{c}i\v{c}, M.~Mihovilovi\v{c}, S.~\v{S}irca, S.~\v{S}tajner \\
{\it J.~Stefan Institute and Dept.~of Physics, University of Ljubljana, Slovenia}
%
\vskip 0.15in
J.~Annand, D.~Hamilton,~D.Ireland \\
{\it University of Glasgow, Glasgow, Scotland,  UK }

\end{center}
