A fundamental and long-standing puzzle in QCD concerns how the intrinsic spins and orbital angular momenta of quarks, and anti-quarks, and gluons make up to the nucleon's 1/2 spin.  Nucleon spin-flavor decomposition is one of the main challenges in our field and  it is one of the main physics programs that have driven the basic design features of JLab-12 GeV upgrade.
%\cite{12GeV_CD0}

This experiment is designed to provide an overwhelming semi-inclusive DIS spin asymmetry data set,  and to investigate nucleon's longitudinal spin, separated into valence and sea quark's contribution.   

The physics goals of this experiment includes:

\begin{itemize}
\item {Provide the world's highest precision data set of polarized neutron ($^3$He) double-spin asymmetry $A_{1n}^h$ in several hadron production channels in semi-inclusive Deep-Inelastic Scattering reactions, with hadron $h=\pi^+, \pi^-, \pi^0, K^+, K^-$,  on a dense grid, over a wide range of ($x, Q^2, z$) and also cover a wide range of hadron transverse momentum $p_T^h$.}    

\item {Investigate the behavior of  $A_{1n}^h$  on its dependency of $Q^2, z$, hadron $p_T^h$ and azimuthal angle $\phi_h$. Compare with the expected behavior from Next-Leading-Order  QCD predictions, identify and pin down the size of the possible higher-twist effects.}

\item { Through the method of Next-Leading-Order (NLO)  QCD global fit , obtain the best knowledge of nucleon spin-flavor decomposition.  Provide experimental evidence to  answer the questions: Are sea quarks polarized ?}

\item { Through the method of Leading-Order ``Purity Method'' obtain 5-flavor nuclear spin decomposition,  as applied in HERMES and COMPASS experiments, obtain piont-to-point extraction on ratios of  $\Delta q/q$ for each quark flavor [$\Delta u/u, \Delta d/d, \Delta \bar{u}/\bar{u},  \Delta \bar{d}/\bar{d}$    and $ (\Delta s+\Delta \bar{s})/(s+\bar{s})$]. }  

\item { Through deliberately  controlled phase space and detection efficiency, obtain high precision results on the charged pion difference asymmetry, $A_{1He}^{\pi^+-\pi^-}$, a charge and flavor non-singlet observable which is only sensitive to valence quark polarization $\Delta d_v - 1/4 \Delta u_v$.  When combined with future JLab  SIDIS data on a polarized proton (NH$_3$ target,  obtain $\Delta u_v$, $\Delta d_v$ and polarized sea flavor asymmetry $\Delta \bar{u}-\Delta \bar{d}$, and its fist moments  $\int  [\Delta \bar{u}(x)-\Delta \bar{d}(x)] dx$. } 

\item { Through high precision SIDIS hadron multiplicity data  within the same experiment setup, on  unpolarized reference cell runs,        carry out a self-consistent simultaneous NLO fit on multiplicity and spin asymmetry to  constrain fragmentation function and parton helicity.    High precision results from this experiment will build into a JLab-12 GeV SIDIS database for future NLO fits, which will also include data from polarized proton and deuteron targets.}
\end{itemize}

This proposal follows the footsteps of earlier JLab-6GeV spin-flavor decomposition proposals 
%\cite{semi-SANE, Hall A}
and an earlier JLab-12 GeV proposal.
%cite PAc34 deferred one 
Using the same high luminosity polarized $^3$He target system and two large acceptance spectrometer combination: BigBite Spectrometer as the electron arm and Super-BigBite Spectrometer (SBS) as the hadron arm,  as in the approved Transversity experiment,  this experiment will be able to collect data in the same run group as the Transversity experiment,  with a longitudinal target spin setting.  The main technical features of this experiment includes:

\begin{itemize}
\item {World highest luminosity polarized  target ($^3$He), with an average polarization of 60$\%$.  }
\item {Two large acceptance magnetic spectrometers, as electron-arm and hadron-arm detect SIDIS in coincidence. The best Figure-Of-Merit for neutron SIDIS spin asymmetries.}
\item{Access the highest $Q^2$ available for SIDIS reactions at  JLab-12 GeV,   complimentary to that of the  SoLID experiment in  Hall A.  At beam energies  of 11 GeV and 8.8 GeV,  provide coverage to a wide range of $Q^2$ , similar to that of CLAS12. }
 \item{Clear particle identification and reliable separation of charged $\pi/K$ over the entire range of hadron momentum through the Ring Imaging Cherenkov detector in SBS.}
  \item{Identical detection phase space for positively-charged  and negatively-charged hadrons, and through SBS magnetic field reversal, a unique feature that is ideal to measure SIDIS yield differences of $\pi^+ -\pi^-$ and the corresponding asymmetries.}  
\end{itemize}

